---
title: 'Get time series '
output:
  html_document:
    df_print: paged
---

COVID 19 number of cases over time 

```{r}
pacman::p_load(lubridate,here,  ggrepel,tidyverse)

```


Now use time series and link to file 

```{r}
url_confirmed <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Confirmed.csv"
url_deaths <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Deaths.csv"
url_recovered <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Recovered.csv"

```

```{r}
n_confirmed <- 
  read_csv(url_confirmed) %>% 
    select(-Lat, -Long) %>% 
    rename(
      lower = `Province/State`,
      higher = `Country/Region`
    ) %>% 
    gather(-lower, -higher, key = "date", value = "n_confirmed") %>% 
    mutate(date = mdy(date))

n_recovered <- 
  read_csv(url_recovered) %>% 
    select(-Lat, -Long) %>% 
    rename(
      lower = `Province/State`,
      higher = `Country/Region`
    ) %>% 
    gather(-lower, -higher, key = "date", value = "n_recovered") %>% 
    mutate(date = mdy(date))

n_deaths <- 
  read_csv(url_deaths) %>% 
    select(-Lat, -Long) %>% 
    rename(
      lower = `Province/State`,
      higher = `Country/Region`
    ) %>% 
    gather(-lower, -higher, key = "date", value = "n_deaths") %>% 
    mutate(date = mdy(date))

tidied_data <- 
  reduce(.x = list(n_confirmed, n_recovered, n_deaths), full_join, by = c("lower", "higher", "date")) %>% 
    gather(key = "type", value = "n", n_confirmed:n_deaths) %>% 
    mutate(type = str_replace(type, pattern = "^n_", ""))


```
Get from series of files 



```{r}
tidied_data %>%
  filter(type == "confirmed") %>%  
  group_by(date) %>% 
  summarise(total_confirmed = sum(n)) %>% 
  ungroup() %>% 
  ggplot(aes(x = date, y = total_confirmed)) + 
  geom_point()  + 
  scale_y_log10()
  

```

Now after Feb 15


```{r, fig.width = 10, fig.height = 8}
tidied_data %>%
  filter(type == "confirmed") %>%  
  filter(date > lubridate::dmy("15-02-2020")) %>% 
  group_by(date) %>% 
  summarise(total_confirmed = sum(n)) %>% 
  ungroup() %>% 
  mutate(week = lubridate::week(date)) %>% 
  ggplot(aes(x = date, y = total_confirmed)) + 
  geom_point()  + 
  scale_y_log10(  
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
    ) + 
  scale_x_date(date_breaks = "1 day") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  stat_smooth(
    aes(group = week),
    method = "lm", se = FALSE
  ) +
  labs(
    x = "Date", y = "Total cases confirmed (log scale)",
    title = "Total worldwide COVID-19 cases confirmed by date after 15 Feb",
    subtitle = "Log scale. Regression lines broken by week",
    caption = "Source: Johns Hopkins CSSE"
  )

ggsave(here("figures", "covid_19_confirmed_from15feb.png"), height = 20, width = 25, units = "cm", dpi = 300)
  
  

```

Let's look some more about what the data could show 


```{r, fig.height = 8, fig.width = 12}
tidied_data %>% 
  mutate(
    place_category = case_when(
      higher == "China" & lower == "Hubei" ~ "Hubei, China",
      higher == "China" & lower != "Hubei" ~ "Rest of China",
      TRUE                                 ~ "Rest of World"
    )
  ) %>% 
  group_by(date, place_category, type) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  ggplot(aes(x = date, y =  n, group = place_category, linetype = place_category)) + 
  facet_wrap(~type) + 
  geom_line() +
  scale_y_log10(    
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
) + labs(
  x = "Date", y = "Number of cases (Log scale)",
  title = "Confirmed cases, deaths, and recovered",
  subtitle = "Hubei, Rest of China, and Rest of World",
  caption = "Source: Johns Hopkins CSSE"
) + 
  scale_linetype_discrete("Location") + 
  theme_minimal()

ggsave(here("figures", "confirmed_deaths_recovered.png"), height = 15, width = 20, units = "cm", dpi = 300)

```

```{r}
# Countries with at least 100 confirmed cases on 8/3/20

big_case_countries <- 
  tidied_data %>% 
    filter(type == "confirmed") %>% 
    group_by(date, higher) %>% 
    summarise(n = sum(n)) %>% 
    ungroup()  %>% 
    filter(date == max(date)) %>% 
    arrange(desc(n)) %>% 
    filter(n > 100) %>% 
    pull(higher)

tidied_data %>% 
  mutate(country = case_when(
    higher %in% big_case_countries ~ higher,
    TRUE                           ~ "Other"
    )
  ) %>% 
  filter(type == "confirmed") %>% 
  group_by(date, country) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  ggplot(aes(x = date, y = n)) + 
  geom_line() +
  scale_y_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  facet_wrap(~country)

ggsave(here("figures", "confirmed_cases_atleast100.png"), height = 25, width = 25, units = "cm", dpi = 300)


```

What's the gradient of increase for these countries since 1 March? 

```{r}
get_gradient_fit <- function(dta){
  num_cases <- dta %>% 
    filter(date == max(date)) %>% 
    pull(n) 
  
  model <- lm(log(n) ~ date, data = dta)
  slope <- coefficients(model)[["date"]]
  rsq <- summary(model)$r.squared
  
  return(tibble(
    num_cases, slope = slope, r_squared = rsq
  ))
}


tidied_data %>% 
  filter(date >= lubridate::dmy("29-02-20")) %>%
  filter(higher %in% big_case_countries) %>% 
  filter(type == "confirmed") %>% 
  filter(!(higher %in% c("Others","Cruise Ship"))) %>% 
  group_by(date, higher) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  group_by(higher) %>% nest() %>% 
  mutate(results = map(data, possibly(get_gradient_fit, otherwise = NA_character_))) %>%
  mutate(results_class = map(results, class)) %>% 
  mutate(results_length = map_dbl(results, length)) %>% 
  filter(results_length == 3) %>% 
  select(higher, results) %>% 
  unnest(results) %>% 
  mutate(is_china = higher == "China") %>% 
  arrange(desc(slope)) %>% 
  ggplot(aes(x = r_squared, y = slope, alpha = log(num_cases))) + 
  geom_point() + 
  theme(legend.position = "none") + 
  scale_x_continuous(limits = c(0.7, 1.0)) +
  geom_text_repel(aes(label = higher), alpha = 1) + 
  labs(
    x = "R-squared (Higher= more log-linear)",
    y = "Slope (Higher= faster % growth rates)",
    title = "Steepness of case growth rate against model fit",
    subtitle = "Countries with at least 100 cases on 8 March 2020. Darker dots = More cases",
    caption = "Source: Johns Hopkins CSSE"
  )

ggsave(here("figures", "rate_of_increase_against_model_fit.png"), height = 20, width = 20, units = "cm", dpi = 300)


```

Look at rate of increase once 100 cases identified 


```{r}
tidied_data %>% 
  filter(type == "confirmed") %>% 
  filter(higher != "Cruise Ship") %>% 
  group_by(higher, date) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  group_by(higher) %>% 
  arrange(date) %>% 
  filter(n >= 100) %>%
  mutate(first_date = date[1]) %>% 
  mutate(days_since_first = date - first_date) %>% 
  mutate(max_days_since_first = max(days_since_first)) %>% 
  ungroup() %>% 
  mutate(country = fct_reorder(higher, desc(max_days_since_first))) %>%
  filter(country != "Others") %>% 
  ggplot(aes(x = days_since_first, y = n)) +
  geom_line() + 
  scale_y_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) + 
  facet_wrap(~country) +
  labs(
    title = "Confirmed cases after first 100 cases",
    subtitle = "Arranged by number of days since 100 or more cases",
    x = "Days after 100 confirmed cases",
    y = "Confirmed cases (log scale)", 
    caption = "Source: Johns Hopkins CSSE"
  )

ggsave("figures/days_since_100.png", height = 20, width = 20, units = "cm", dpi = 300)

```


Alternative presentation (from [here](https://github.com/gorkang/2020-corona/blob/master/2020-corona-plot.R))

```{r}
days_since_data <- 
  tidied_data %>% 
    filter(type == "confirmed") %>% 
    filter(higher != "Cruise Ship") %>% 
    group_by(higher, date) %>% 
    summarise(n = sum(n)) %>% 
    ungroup() %>% 
    group_by(higher) %>% 
    arrange(date) %>% 
    filter(n >= 100) %>%
    mutate(first_date = date[1]) %>% 
    mutate(days_since_first = date - first_date) %>% 
    mutate(max_days_since_first = max(days_since_first)) %>% 
    ungroup() %>% 
    mutate(country = fct_reorder(higher, desc(max_days_since_first))) %>%
    mutate(country_label = glue::glue("{country}, {max_days_since_first} days")) %>% 
    filter(country != "Others") 

days_since_data %>% 
  ggplot(aes(x = days_since_first, y = n, group = country, colour = country_label)) +
  geom_line() + 
  ggrepel::geom_text_repel(aes(label = country_label), show.legend = FALSE, segment.color = "grey", nudge_x = 10,  
                            data = days_since_data %>% 
                              group_by(country) %>% 
                              filter(days_since_first == max(days_since_first)) %>% 
                              filter(days_since_first >= 10)
                            ) +
  scale_y_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) + 
  labs(
    title = "Confirmed cases after first 100 cases",
    subtitle = "Arranged by number of days since 100 or more cases. Countries with 10 or more days labelled",
    x = "Days after 100 confirmed cases",
    y = "Confirmed cases (log scale)", 
    caption = "Source: Johns Hopkins CSSE"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none"
  ) 

ggsave(here("figures", "days_since_100_oneplot.png"), height = 15, width = 25, units = "cm", dpi = 300)


```

Let's try to model this (China and not China to start with)

```{r}
tidied_data %>% 
  mutate(
    place_category = case_when(
      higher == "China" & lower == "Hubei" ~ "Hubei, China",
      higher == "China" & lower != "Hubei" ~ "Rest of China",
      TRUE                                 ~ "Rest of World"
    )
  ) %>% 
  group_by(date, place_category, type) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  filter(n >= 100) %>% 
  ggplot(aes(x = date, y = n, group = type, linetype = type)) + 
  geom_line() + 
  facet_wrap(~place_category) + 
  scale_y_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  labs(
    y = "Number of cases", 
    x = "Date",
    title = "Confirmed, Recovered, Deaths",
    caption = "Source: Johns Hopkins CSSE"
  )


ggsave(here("figures", "confirmed_deaths_recovered_china_elsewhere.png"), height = 20, width = 30, units = "cm", dpi = 300)
```


# Lagged association between deaths and confirmed cases, Hubei

For how many days is there a deaths data series? (from 10^2 cases?) 

Then work out how many days confirmed cases to include 

```{r}
tidied_data %>% 
  mutate(
    place_category = case_when(
      higher == "China" & lower == "Hubei" ~ "Hubei, China",
      higher == "China" & lower != "Hubei" ~ "Rest of China",
      TRUE                                 ~ "Rest of World"
    )
  ) %>% 
  filter(type != "recovered") %>% 
  group_by(date, place_category, type) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  filter(place_category == "Hubei, China") %>% 
  group_by(type) %>% 
  arrange(date) %>% 
  mutate(days_since_start = date - date[1]) %>% 
  ggplot(aes(x = days_since_start, y = n, linetype = type, group = type)) +
  geom_line() + 
  scale_y_log10(
    breaks = 10^(1:7), 
    minor_breaks = 10 ^ seq(1, 7, by = 0.1),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
    
  )

```
Exponent looks like 4.84 for confirmed cases, and 3.50 for deaths (at end of series). This gives a case fatality rate of around 4.6%, so slightly higher than before (based on slightly earlier data, and for whole of China).

Let's check this by overlaying both 


```{r}
tidied_data %>% 
  mutate(
    place_category = case_when(
      higher == "China" & lower == "Hubei" ~ "Hubei, China",
      higher == "China" & lower != "Hubei" ~ "Rest of China",
      TRUE                                 ~ "Rest of World"
    )
  ) %>% 
  filter(type != "recovered") %>% 
  group_by(date, place_category, type) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  filter(place_category == "Hubei, China") %>% 
  group_by(type) %>% 
  arrange(date) %>% 
  mutate(days_since_start = date - date[1]) %>%
  ungroup() %>% 
  mutate(log_n = log(n, 10)) %>%
  ggplot(aes(x = days_since_start, y = log_n, linetype = type, group = type)) +
  geom_line() +
  geom_line(aes(x = days_since_start, y = log_n - (4.84 - 3.50)),
            colour = "red", linetype = "dotdash",
            data = 
              tidied_data %>% 
                mutate(
                  place_category = case_when(
                    higher == "China" & lower == "Hubei" ~ "Hubei, China",
                    higher == "China" & lower != "Hubei" ~ "Rest of China",
                    TRUE                                 ~ "Rest of World"
                  )
                ) %>% 
                filter(type == "confirmed") %>% 
                group_by(date, place_category, type) %>% 
                summarise(n = sum(n)) %>% 
                ungroup() %>% 
                filter(place_category == "Hubei, China") %>% 
                group_by(type) %>% 
                arrange(date) %>% 
                mutate(days_since_start = date - date[1]) %>%
                ungroup() %>% 
                mutate(log_n = log(n, 10))
              )

```

Let's see what a linear regression of deaths on confirmed cases predicts 

```{r}
hb_log_mod <- 
tidied_data %>% 
  mutate(
    place_category = case_when(
      higher == "China" & lower == "Hubei" ~ "Hubei, China",
      higher == "China" & lower != "Hubei" ~ "Rest of China",
      TRUE                                 ~ "Rest of World"
    )
  ) %>% 
  filter(type != "recovered") %>% 
  group_by(date, place_category, type) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  filter(place_category == "Hubei, China") %>% 
  select(-place_category) %>% 
  spread(type, n) %>% 
  lm(log(deaths, 10) ~ log(confirmed, 10), data =. ) 

hb_log_mod %>% 
  summary()

```
```{r}
wide_hb_data <-  
  tidied_data %>% 
    mutate(
      place_category = case_when(
        higher == "China" & lower == "Hubei" ~ "Hubei, China",
        higher == "China" & lower != "Hubei" ~ "Rest of China",
        TRUE                                 ~ "Rest of World"
      )
    ) %>% 
    filter(type != "recovered") %>% 
    group_by(date, place_category, type) %>% 
    summarise(n = sum(n)) %>% 
    ungroup() %>% 
    filter(place_category == "Hubei, China") %>% 
    select(-place_category) %>% 
    spread(type, n) 

wide_hb_data  
```


```{r}
wide_hb_data %>% 
  mutate(prediction = 10 ^ predict(hb_log_mod, .)) %>% 
  mutate(eyeballing = confirmed *  10 ^ -(4.84 - 3.50)) %>% 
  gather(-date, key = "type", value = "n") %>% 
  mutate(type = case_when(
    type == "confirmed" ~ "Confirmed Cases", 
    type == "deaths"   ~ "Confirmed Deaths",
    type == "prediction" ~ "Predicted Deaths (Linear regression)",
    type == "eyeballing" ~ "Predicted Deaths (Eyeballing latest values)"
  )) %>% 
  ggplot(aes(x = date, y= n, linetype = type, colour = type)) + 
  geom_line() +
  scale_y_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  scale_colour_manual(values = c("black", "black", "red", "green")) +
  scale_linetype_manual(values = c("solid", "dotdash", "dashed", "dashed")) + 
  labs(
    title = "Relationship between confirmed cases and confirmed deaths, Hubei, China",
    caption = "Model prediction formula within lm: log(deaths, 10) ~ log(confirmed, 10)",
    subtitle = "Predicted mortality rate: 4.3%, Adjusted R-squared of fit: 0.98",
    x = "Date", 
    y = "Number of cases",
    linetype = "Case/Prediction type",
    colour = "Case/Prediction type"
  ) + 
  theme_minimal()

ggsave(here("figures", "hubei_case_mort_pred.png"), height = 15, width = 25, units = "cm")

```



And in reverse? 

```{r}
hb_log_mod_rev <- 
tidied_data %>% 
  mutate(
    place_category = case_when(
      higher == "China" & lower == "Hubei" ~ "Hubei, China",
      higher == "China" & lower != "Hubei" ~ "Rest of China",
      TRUE                                 ~ "Rest of World"
    )
  ) %>% 
  filter(type != "recovered") %>% 
  group_by(date, place_category, type) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  filter(place_category == "Hubei, China") %>% 
  select(-place_category) %>% 
  spread(type, n) %>% 
  lm(log(confirmed, 10) ~ log(deaths, 10), data =. ) 

hb_log_mod_rev %>% 
  summary()


```

So this can be used to predict the number of confirmed cases against the number of deaths if the correspondence between confirmed cases and confirmed deaths were the same as in the Hubei. 

```{r}
tidied_data %>% 
  filter(higher == "United Kingdom") %>% 
  filter(type != "recovered") %>% 
  group_by(date, type) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  spread(type, n)  %>% 
  filter(deaths >= 5) %>% 
  mutate(
    predicted_confirmed = 10^predict(hb_log_mod_rev, newdata = .)
  ) %>% 
  gather(key = "type", value = "n", -date) %>% 
  ggplot(aes(x = date, y = n, group = type, linetype = type, colour = type)) + 
  geom_line()  + 
  scale_colour_manual(values = c("black", "red", "black")) + 
  scale_linetype_manual(values = c("solid", "solid", "dashed")) + 
  scale_y_log10(breaks = c(5, 10, 20, 50, 100, 200, 500, 1000, 2000, 5000, 10000, 20000, 50000, 100000)) +
  labs(
    x = "Date",
    y = "Number of cases (log scale)",
    title = "UK: Confirmed cases, confirmed deaths,
    and predicted number of cases based on number of deaths",
    subtitle = "Predicted number of cases made by assuming the correspondence between confirmed cases and
    confirmed deaths observed in Hubei, China, also applies to other countries",
    caption = "From first date where five or more cumulative confirmed deaths were recorded in the UK"
  )

ggsave(here("figures", "uk_confirmed_predicted_from_hubei.png"), height = 15, width = 20, units = "cm", dpi = 300)

```


And what about Italy and the USA?

```{r}
tidied_data %>% 
  filter(higher == "Italy") %>% 
  filter(type != "recovered") %>% 
  group_by(date, type) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  spread(type, n)  %>% 
  filter(deaths >= 5) %>% 
  mutate(
    predicted_confirmed = 10^predict(hb_log_mod_rev, newdata = .)
  ) %>% 
  gather(key = "type", value = "n", -date) %>% 
  ggplot(aes(x = date, y = n, group = type, linetype = type, colour = type)) + 
  geom_line()  + 
  scale_colour_manual(values = c("black", "red", "black")) + 
  scale_linetype_manual(values = c("solid", "solid", "dashed")) + 
  scale_y_log10(breaks = c(5, 10, 20, 50, 100, 200, 500, 1000, 2000, 5000, 10000, 20000, 50000, 100000),
                labels = c("5", "10", "20","50","100","200","500","1000", "2000","5000","10,000","20,000","50,000","100,000")
                ) +
  scale_x_date(minor_breaks = "1 day")+
  labs(
    x = "Date",
    y = "Number of cases (log scale)",
    title = "Italy: Confirmed cases, confirmed deaths,
    and predicted number of cases based on number of deaths",
    subtitle = "Predicted number of cases made by assuming the correspondence between confirmed cases and
    confirmed deaths observed in Hubei, China, also applies to other countries",
    caption = "From first date where five or more cumulative confirmed deaths were recorded in Italy"
  ) + 
  annotate(geom = "rect", xmin = dmy("04-03-2020"), xmax = dmy("06-03-2020"), ymin = 2000, ymax = 10000, alpha = 0.2, fill = "darkgreen")

ggsave(here("figures", "italy_confirmed_predicted_from_hubei.png"), height = 15, width = 20, units = "cm", dpi = 300)

```
```{r}
tidied_data %>% 
  filter(higher == "US") %>% 
  filter(type != "recovered") %>% 
  group_by(date, type) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  spread(type, n)  %>% 
  filter(deaths >= 5) %>% 
  mutate(
    predicted_confirmed = 10^predict(hb_log_mod_rev, newdata = .)
  ) %>% 
  gather(key = "type", value = "n", -date) %>% 
  ggplot(aes(x = date, y = n, group = type, linetype = type, colour = type)) + 
  geom_line()  + 
  scale_colour_manual(values = c("black", "red", "black")) + 
  scale_linetype_manual(values = c("solid", "solid", "dashed")) + 
  scale_y_log10(breaks = c(5, 10, 20, 50, 100, 200, 500, 1000, 2000, 5000, 10000, 20000, 50000, 100000),
                labels = c("5", "10", "20","50","100","200","500","1000", "2000","5000","10,000","20,000","50,000","100,000")
                ) +
  scale_x_date(minor_breaks = "1 day")+
  labs(
    x = "Date",
    y = "Number of cases (log scale)",
    title = "USA: Confirmed cases, confirmed deaths,
    and predicted number of cases based on number of deaths",
    subtitle = "Predicted number of cases made by assuming the correspondence between confirmed cases and
    confirmed deaths observed in Hubei, China, also applies to other countries",
    caption = "From first date where five or more cumulative confirmed deaths were recorded in the USA"
  ) + 
  annotate(geom = "rect", xmin = dmy("08-03-2020"), xmax = dmy("10-03-2020"), ymin = 200, ymax = 1000, alpha = 0.2, fill = "darkgreen")

ggsave(here("figures", "us_confirmed_predicted_from_hubei.png"), height = 15, width = 20, units = "cm", dpi = 300)

```



Now to generalise. 

For all countries with at least 10 recorded deaths, and from the date of 10 deaths or more, what is the number of confirmed cases, and what would the predicted number of confirmed cases be if the correspondence between the number of cases and the number of deaths were as it has been in Hubei, China? 

* To DO! 


```{r}
predicted_cases_after_10_deaths <- 
  tidied_data %>% 
    filter(higher != "China") %>% 
    group_by(higher, date, type) %>% 
    summarise(n = sum(n)) %>% 
    ungroup() %>%
    spread(type, n) %>% 
    filter(deaths >= 10) %>% 
    group_by(higher) %>% 
    mutate(days_since_10_deaths = date - min(date)) %>% 
    nest() %>% 
    mutate(predicted_confirmed = map(data, ~broom::augment(x = hb_log_mod_rev, newdata = .))) %>% 
    select(-data) %>% 
    unnest(predicted_confirmed) %>% 
    mutate(
      pred_confirmed = 10 ^ .fitted,
      pred_lower     = 10 ^ (.fitted - 2 * .se.fit),
      pred_higher    = 10 ^ (.fitted + 2 * .se.fit)
    ) %>% 
  select(higher, date, pred_confirmed, pred_lower, pred_higher)

tidied_data %>% 
  group_by(higher, date, type) %>% 
    summarise(n = sum(n)) %>% 
    ungroup() %>%
    spread(type, n) %>% 
  filter(confirmed >= 100) %>% 
  left_join(predicted_cases_after_10_deaths) %>% 
  filter(higher != "Cruise Ship") %>% 
  filter(higher != "China") %>% 
  group_by(higher) %>% 
  mutate(number_valid = sum(!is.na(pred_confirmed))) %>% 
  filter(number_valid >= 7) %>% 
  mutate(
    country = fct_reorder(higher, -number_valid)
  ) %>% 
  ggplot(aes(x = date)) + 
  geom_line(aes(y = confirmed)) +
  facet_wrap(~country) + 
  scale_y_log10(
    breaks = c(
      10, 20, 50, 
      100, 200, 500,
      1000, 2000, 5000,
      10000, 20000, 50000,
      100000, 200000, 500000,
      1000000
      ),
    labels  = c(
      "10", "20", "50", 
      "100", "200", "500", 
      "1000", "2000", "5000",
      "10k", "20k", "50k",
      "100k", "200k", "500k",
      "1M"
    )
  ) +
  geom_line(aes(y = pred_confirmed), colour = "blue") + 
  geom_ribbon(aes(ymin = pred_lower, ymax = pred_higher), alpha = 0.5) +
  scale_x_date(date_labels = "%e %b") + 
  labs(
    title = "Cases Confirmed, and predicted from numbers of confirmed deaths", 
    subtitle = "Black line: Confirmed cases. Blue line: predicted from deaths",
    y = "Number of cases",
    x = "Date",
    caption = "Countries shown are those where it was at least a week since 10 deaths were observed, arranged by number of days since this milestone was reached. 
    Prediction on association between log deaths and log cases in Hubei, China. Source: Johns Hopkins CSSE"
  )
  
ggsave(here("figures", "confirmed_against_predicted_from_deaths.png"), height = 20, width = 30, dpi = 300, units = "cm")

```