---
title: "Geomapping using latlong data"
output: html_notebook
---


# Aim

To use the long-lat data to create maps of covid expansion from the CSSE dataset 

To make this interactive? 


# Packages 


```{r}
pacman::p_load(
  tidyverse, 
  googleway,
  tidyverse, 
  ggrepel,
  ggspatial,
  libwgeom,
  sf,
  rnaturalearth,
  rnaturalearthdata,
  wbstats
  
  
  
  
               )
```


```{r}
url_confirmed <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Confirmed.csv"
url_deaths <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Deaths.csv"
url_recovered <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Recovered.csv"

```


```{r}
n_confirmed <- 
  read_csv(url_confirmed) %>% 
    rename(
      lower = `Province/State`,
      higher = `Country/Region`
    ) %>% 
    gather(-lower, -higher, -Lat, -Long, key = "date", value = "n_confirmed") %>% 
    mutate(date = mdy(date))

n_recovered <- 
  read_csv(url_recovered) %>% 
    rename(
      lower = `Province/State`,
      higher = `Country/Region`
    ) %>% 
    gather(-lower, -higher, -Lat, -Long, key = "date", value = "n_recovered") %>% 
    mutate(date = mdy(date))

n_deaths <- 
  read_csv(url_deaths) %>% 
    rename(
      lower = `Province/State`,
      higher = `Country/Region`
    ) %>% 
    gather(-lower, -higher, -Lat, -Long, key = "date", value = "n_deaths") %>% 
    mutate(date = mdy(date))

tidied_data <- 
  reduce(.x = list(n_confirmed, n_recovered, n_deaths), full_join, by = c("lower", "higher", "date", "Lat", "Long")) %>% 
    gather(key = "type", value = "n", n_confirmed:n_deaths) %>% 
    mutate(type = str_replace(type, pattern = "^n_", ""))


```
```{r}
theme_set(theme_bw())

```


```{r}
tidied_data %>% 
  filter(date == max(date)) %>% 
  filter(!is.na(higher) & is.na(lower)) %>% 
  ggplot(aes(x = Long, y= Lat, size = n, colour = type, colour = type)) +
  geom_point()
  
```


```{r}
# ?ne_countries 
world <- ne_countries(scale = "medium", returnclass = "sf")
class(world)
```

Visualise 

```{r}
world %>% 
  ggplot() + 
  geom_sf()

```


```{r}

ggplot(data = world) +
    geom_sf() +
    geom_point(data = tidied_data, aes(x = Long, y = Lat, size = n, colour = type))

```


And only for 'higher'

```{r}

ggplot(data = world) +
    geom_sf() +
    geom_point(data = tidied_data %>% 
                 filter(is.na(lower) & !is.na(higher)), 
               aes(x = Long, y = Lat, size = n, colour = type))


```

Let's now try to join using some of the motion chart code used previously


```{r}

dta_country_continent_lookup <- read_csv("https://datahub.io/JohnSnowLabs/country-and-continent-codes-list/r/country-and-continent-codes-list-csv.csv") %>% 
  mutate(
    Continent_Code = case_when(
      is.na(Continent_Code) ~ "NA", # NA was mis-parsed as NA rather than "NA" - North America!
      TRUE                  ~ Continent_Code
    )
  )

# There's some matching work required 
tidied_country_continent_lookup <- 
  dta_country_continent_lookup %>% 
    mutate(
      stripped_name = map_chr(Country_Name, str_extract, pattern = "^[^,]+"),
      special_name  = case_when(
        Country_Name == "Taiwan"                                        ~ "Taiwan*",
        Country_Name == "Korea, Democratic People's Republic of"        ~ "Korea, North",
        Country_Name == "Korea, Republic of"                            ~ "Korea, South",
        TRUE                                                            ~ NA_character_
      ),
      name_to_match = coalesce(special_name, stripped_name) # First special name, then if NA stripped name
    ) 

tidied_country_continent_lookup
```

And population (using wbstats package)

```{r, cache = TRUE}

pop_wb <- wb(indicator = "SP.POP.TOTL") 


```
Can't get that to work, tried twice. But not essential. 


```{r, eval = FALSE}

code_population <- 
  pop_wb %>%
    mutate(date = as.numeric(date)) %>% 
    group_by(iso3c) %>% 
    filter(date == max(date)) %>% 
    ungroup() %>% 
    select(country_code = iso3c, population = value)

code_population

```

So, let's try to match on this 

```{r, eval = FALSE}
country_tidied_data <- 
  tidied_data %>% 
  group_by(higher, date, type) %>% 
  summarise(n = sum(n)) %>% 
  ungroup() %>% 
  rename(country = higher)

country_tidied_data
```

Now let's try to join and see what still remains 


```{r}

# tidied_country_continent_lookup %>% 
#   left_join(code_population, by = c("Three_Letter_Country_Code" = "country_code"))

spat_tidied_data <- 
  tidied_data %>% 
    group_by(higher, Lat, Long, date, type) %>% 
    summarise(n = sum(n)) %>% 
    ungroup() %>% 
    rename(country = higher) %>% 
    left_join(
      tidied_country_continent_lookup,
      by = c("country" = "name_to_match")
    ) %>%  
    left_join(world, by = c("Three_Letter_Country_Code" = "wb_a3")) # there are a number of three letter country code, but using this for now

spat_tidied_data
```

Now to plot as choropleth

```{r}
spat_tidied_data %>% 
  filter(date == max(date)) %>% 
  filter(type.x == "confirmed") %>% 
  ggplot() + 
  geom_sf(aes(geometry = geometry, fill = n)) + 
  scale_fill_viridis( trans = "log10")

```